Learning Programs through Bayesian Inference and Planning

### 2013-10-21 drafts/nips/nips2013.tex
Progress on NIPS draft

>>>>

\section{Introduction}

Motivation: Many approaches to constructive machine learning use structured representations, such as graphs, grammars, Horn clauses, relations, ..., ???. All of these may be thought of as a program - programs are at least as expressive as these other representations.

% TODO: Sequential EC? SEC? What is a good name for this?
The space of programs is enormous and inherently unpredictable \cite{PACunpredictability}.
We introduce a new algorithm, SEC, for searching the space of programs.
Two main ideas underly SEC:
\begin{itemize}
\item \emph{Learning to search}: Programs admit compositionality and reuse of subprograms. SEC exploits this compositionality to learn a library of program fragments, which it then reuses when performing further searches for programs.
In a multitask setting, this permits bootstrap learning of more complicated programs after the synthesis of simpler programs.
\item \emph{Incremental Program Synthesis}: In many search problems, there is a natural means of assigning partial credit for partially-correct solutions. SEC uses this partial credit to select promising programs and modify them, creating complicated programs step-by-step.
Rather than using a mutation operator, as in genetic programming, or Metropolis-Hastings proposals, as in \cite{MHprogramInduction}, SEC uses function composition to combine smaller programs in to larger ones.
\end{itemize}

The SEC algorithm comes from a generative model over compositions of functions drawn from a stochastic grammar over programs.
We describe this model, as well as how we perform inference, in ...

SEC treats planning as an inference problem.

\section{The SEC Algorithm}
\subsection{Generative Model}
\subsection{Inference}
\subsection{Program Representation}

\section{Application to Structure Learning}

\subsection{Graph Combinators}

\subsection{Learning Graphical Models}

\section{Building Towers in Blocks World}

\subsection{The Blocks World Domain}

\subsection{Learned Tower programs}

\section{Discussion}

\subsection{Relation to Prior Work}

\subsection{Limitations of SEC}
